### 2022-05-27 Publish Paper/manuscript_title_etc.tex
Update eng paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
Nowadays, the dramatic development of the big city and industrial zones leads to a higher rate of skin disease because of polluted air. Moreover, in many developing countries, the hospital is being overloaded every single day by the huge number of the patient. They need a fast and accurate solution to diagnose skin disease before meeting the doctor or how to create an optimized and balanced model for skin lesion classification. After the literature review process, I found that there are many outstanding papers on both Deep Learning and Machine Learning. In Deep Learning, they often use transfer learning. Some new approaches are GradCam, Kernel Shap, Student and Teacher model. In Machine Learning, Random Forest, and Support Vector Machine are applied. The main focus of this research is to analyze the effect of metadata on the combination of the backbone model and the Soft-Attention layer. The soft-Attention layer is tested in a previous paper that improve the model performance to 92 percent accuracy. I also try some other combinations to construct an optimized model that can use on mobile phone. After the experiment process, I found out that metadata and weighted loss function makes the performance of the model less imbalanced with 90 percent accuracy but its f1-score and recall score standard deviation is 0.08 and 0.09, respectively. I also construct a model with the combination of MobileNetV3Large and Soft-Attention layer with image and metadata input with 86 percent accuracy but thirty times as fast as the highest performance model.
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
Today, the rapid development of industrial zones leads to an increasing incidence of skin diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffered from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels have lack of experience, having a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions and tools to support the diagnosis of skin diseases have been researched and developed. These include DenseNet, InceptionNet, ResNet, NasNet, SeNet, EfficientNet, VGGNet. In this study, another approach to build tools to aid in the diagnosis of skin pathologies is proposed. SOTA (state of the art) models DenseNet, InceptionNet, ResNet, NasNet, MobileNet combined with Soft-Attention are used as backbone. In addition, personal information such as age and gender are also used. In addition, a new loss function that takes into account the imbalance of the data is also proposed. Experimental results on dataset HAM10000 show that using InceptionResNetV2 with Soft-Attetion and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and auc- scores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published indexes. Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of floors is 4 times less, it achieves 86 percent accuracy and 30 times faster diagnosis.
}
